---
title: "Fractional performance"
author: "Heejung Jung"
date: "10/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"""
* load libraries
* load all of the data as saxe, spunt, posner, memory
* plot covariance

TODO: Oct 21
1. Histogram for all participants. 
2. Correlation grids (row: spunt, saxe, memory, posner)
   Plot of the mean (performance and RT) for each participant - variation between individual 
3. Fractional any (packages  out there?)
4. Download HCP. 


"""
```{r load_libraries, include=FALSE}
library(MASS)
library(tidyverse)
library(GGally)
library(stringr)
library(psych)
library(car)
library(ggplot2)
library(ggpubr)
library(ggridges)
library(dplyr)
library(ggcorrplot)
```


"""
tom-saxe
accuracy

tomspunt
accuracy

posner
accuracy

memory_test_*
test_accuracy
"""

/Users/h/Dropbox/projects_dropbox/analysis_fractional/data/dartmouth/d02_preprocessed/sub-0003




### FUNCTION: expect_df load data
```{r expect dataframe, include=FALSE}
load_df = function(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE ) {
  # task-fractional_run-02-memory_beh
  # INPUT:
  # * TASKNAME (e.g. pain, cognitive, vicarious)
  # * SUBJECT_VARKEY (e.g. src_subject_id or subject)
  # A. load data ______________________________________________________________
  FILENAME = paste('*_task-fractional_*' ,TASKNAME, '*_beh.csv', sep = "")
  common_path = Sys.glob(file.path(main_dir,'data', 'dartmouth', 'd02_preprocessed',
                                   'sub-*',FILENAME))
  filter_path = common_path[!str_detect(common_path,pattern="sub-0001")]
  
  DF <- do.call("rbind",lapply(filter_path,FUN=function(files){ read.csv(files)}))
  is.nan.data.frame <- function(x)
    do.call(cbind, lapply(x, is.nan))
  DF[is.nan(DF)] <- NA
  # subjects as factor
  #print("subject")
  DF[,"subject"] = factor(DF[,SUBJECT_VARKEY])
  DF[,"task"] = TASKNAME
  # print("line323")
  # B. plot expect rating NA ___________________________________________________
  DF_expect_NA = aggregate(DF[,DV], list(DF$subject),function(x) sum(is.na(x)))
  
  DF_remove_NA = DF[!is.na(  DF[DV]  ),]
  
  DATA <- as.data.frame(DF_remove_NA)
}
```

```{r plot rt distribution, include=FALSE}
plot_dist = function(DF, X, Y, KEYWORD, LABEL, XLAB, YLAB){
  ggplot(  DF,aes(x = DF[,X], y = DF[,Y])  ) +
    geom_density_ridges_gradient(aes(fill = ..x..), scale = 3, size = 0.3    ) +
    scale_fill_gradientn(colours = c("#0D0887FF", "#CC4678FF", "#F0F921FF"),name = LABEL) +
    ggtitle(KEYWORD) + xlab(XLAB) + ylab(YLAB) 
}
```

# parameters

```{r main directory}
main_dir = dirname(getwd())
```

```{r load_memory, include=FALSE}
TASKNAME = 'memory_test*'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "test_accuracy"
MEMORY = load_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE)

MEMORY$accuracy = 0
MEMORY$accuracy[MEMORY$param_answer== 1 & MEMORY$event03_response_key== 1] <- 1
MEMORY$accuracy[MEMORY$param_answer== 0 & MEMORY$event03_response_key== 0] <- 1
MEMORY$accuracy[is.na(MEMORY$event03_RT) ] <- NA
```

```{r load_posner, include=FALSE}
TASKNAME = 'posner'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "accuracy"
POSNER = load_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE)

POSNER$accuracy = 0
POSNER$accuracy[POSNER$param_target_location== "left" & POSNER$event04_response_keyname== "left"] <- 1
POSNER$accuracy[POSNER$param_target_location== "right" & POSNER$event04_response_keyname== "right"] <- 1
POSNER$accuracy[is.na(POSNER$event04_RT) ] <- NA
```

```{r load_spunt, include=FALSE}
TASKNAME = 'tomspunt'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "accuracy"
SPUNT = load_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE)

# TODO: update this later in the script, but temporarily, fix the accuracy scores here.
SPUNT$accuracy = 0
SPUNT$accuracy[SPUNT$param_normative_response == 1 & SPUNT$event03_response_key == 1] <- 1
SPUNT$accuracy[SPUNT$param_normative_response == 2 & SPUNT$event03_response_key == 3] <- 1
SPUNT$accuracy[is.na(SPUNT$event03_response_onset) ] <- NA
```

```{r load_saxe, include=FALSE}
TASKNAME = 'tomsaxe'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "accuracy"
SAXE = load_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE)
SAXE$accuracy = 0
SAXE$accuracy[SAXE$answer == 1 & SAXE$event04_response_key == 1] <- 1
SAXE$accuracy[SAXE$answer == 2 & SAXE$event04_response_key == 2] <- 1
SAXE$accuracy[is.na(SAXE$event04_response_onset) ] <- NA
```






# mean per participant and covariance ____________________________________________________________________________________

TODO
```{r function: subjectwise mean}
subjectwise_mean = function(DF, GROUPBY, DV, DF_NAME){
DF %>%
  group_by(.data[[GROUPBY]]) %>%
  summarise(performance = sum(.data[[DV]]), 
            count = n() ) %>%
 group_by(.data[[GROUPBY]]) %>%
 mutate(percentage = 100* performance/count)

DF <-  as.data.frame(DF)
}

```
```{r}
memory_perf = subjectwise_mean(MEMORY, "subject", "test_accuracy", "")
```

# select subset of data from each task
```{r dplyr_subset, include=FALSE}

memory_perf = MEMORY %>%
  group_by(subject) %>%
  summarise(performance = sum(accuracy, na.rm = TRUE), 
            count = sum(!is.na(accuracy)) ) %>%
 group_by(subject) %>%
 mutate(percentage = 100* performance/count)

spunt_perf = SPUNT %>%
  group_by(subject) %>%
  summarise(performance = sum(accuracy, na.rm = TRUE), 
            count = sum(!is.na(accuracy)) ) %>%
 group_by(subject) %>%
 mutate(percentage = 100* performance/count)

saxe_perf = SAXE %>%
  group_by(subject) %>%
  summarise(performance = sum(accuracy, na.rm = TRUE), 
            count = sum(!is.na(accuracy)) ) %>%
 group_by(subject) %>%
 mutate(percentage = 100* performance/count)

posner_perf = POSNER %>%
  group_by(subject) %>%
  summarise(performance = sum(accuracy, na.rm = TRUE), 
            count = sum(!is.na(accuracy)) ) %>%
 group_by(subject) %>%
 mutate(percentage = 100* performance/count)


memory_perf$task = "memory"
spunt_perf$task = "spunt"
saxe_perf$task = "saxe"
posner_perf$task = "posner"
```


```{r}
FULL_PERF = memory_perf %>%
    full_join(spunt_perf, by='subject') %>%
    full_join(saxe_perf, by='subject') %>%
    full_join(posner_perf, by = 'subject')

```

```{r}
names(FULL_PERF)[names(FULL_PERF) == "performance"] <- "memory"
names(FULL_PERF)[names(FULL_PERF) == "performance"] <- "spunt"
names(FULL_PERF)[names(FULL_PERF) == "performance"] <- "saxe"
names(FULL_PERF)[names(FULL_PERF) == "performance"] <- "posner"
memory_perf$performance <- unlist(memory_perf$performance)
spunt_perf$performance <- unlist(spunt_perf$performance)
saxe_perf$performance <- unlist(saxe_perf$performance)
posner_perf$performance <- unlist(posner_perf$performance)

```

```{r}
names(FULL_PERF)[names(FULL_PERF) == "percentage.x"] <- "memory"
names(FULL_PERF)[names(FULL_PERF) == "percentage.y"] <- "spunt"
names(FULL_PERF)[names(FULL_PERF) == "percentage.x.x"] <- "saxe"
names(FULL_PERF)[names(FULL_PERF) == "percentage.y.y"] <- "posner"
```
# plot performancee distribution ________________________________________________________________________________
```{r plot distribution}
combinedDf <- rbind(memory_perf, spunt_perf, saxe_perf, posner_perf)
# plot_dist(memory_perf, "perf", "subject", "Fractional: Memory",    "RT (s)", "Performance",  "subject")
# plot_dist(saxe_perf,   "perf", "subject", "Fractional: ToM Saxe",  "RT (s)", "Performance",  "subject")
# plot_dist(spunt_perf,  "perf", "subject", "Fractional: ToM Spunt", "RT (s)", "Performance",  "subject")
# plot_dist(posner_perf, "perf", "subject", "Fractional: Posner",    "RT (s)", "Performance",  "subject")
plot_dist(data.frame(combinedDf), "percentage", "task", "Fractional", "per (%)", "task performance (percentage)", "task")
```



# plot Performance Covariance matrix ________________________________________________________________________________

https://arxiv.org/pdf/1201.2577.pdf
```{r}

cov_perf= FULL_PERF %>% select(memory, posner, saxe, spunt, subject )
C2 = cor(cov_perf[1:4], use = "pairwise.complete.obs")
C2
```

# spearman rho
```{r}
C2 = cor(cov_perf[1:4], use = "pairwise.complete.obs", method = "spearman")
ggcorrplot(C2)
```

# pearson correlation
```{r}
C2 = cor(cov_perf[1:4], use = "pairwise.complete.obs", method = "pearson")
ggcorrplot(C2)
```


```{r}
ggpairs(cov_perf[,c(2:5)], 
        pch = 19, 
        columnLabels = c( "memory", "posner", "saxe", "spunt"), 
        title = "correlation matrix of tasks", 
          upper = list(continuous =wrap(ggally_cor, displayGrid = FALSE), combo = "box_no_facet", discrete = "facetbar", na =
    "na"),)
```


